### 2011-08-27 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress.

@@

@@

TODO with the best IH from the previous step, how about using Random as CH?

>>>>

TODO interpretation - GLPK wins all the time, takes 1 second, which is OK.

@@

TODO count improvement, from there count average + stdev of improvement for every (data set, IH)

TODO we will ignore RandomRemove and RemoveWorst, they cannot help us

\begin{table}
  \caption{Best IH for \heu{Glpk}}
  \bigskip
  \label{table-experiments-best-ih-for-glpk}
  \centering
  \begin{tabular}{l || l | l || l | l}
    Data set & \heu{Hungry} & \heu{Hungry} & \heu{Crossover} & \heu{Crossover} \\
     & improvement & improvement & improvement & improvement \\
     & avg & stdev & avg & stdev \\
    \hline
    \dataset{80-320} & 0.00017 & 0.00118 & 0.00017 & 0.00118 \\
    \dataset{90-405} & 0.00502 & 0.00618 & 0.00033 & 0.00165 \\
    \dataset{100-500} & 0.00664 & 0.00667 & 0.00016 & 0.00081 \\
    \hline
    \dataset{100-100} & 0.00000 & 0.00000 & 0.00000 & 0.00000 \\
    \dataset{100-200} & 0.00000 & 0.00000 & 0.00000 & 0.00000 \\
    \dataset{100-1000} & 0.01630 & 0.01294 & 0.00180 & 0.00506 \\
  \end{tabular}    
	% TODO separate somehow
  \begin{tabular}{l || l | l || l | l}
    Data set & \heu{LB} & \heu{LB} & \heu{Mutation} & \heu{Mutation} \\
     & improvement & improvement & improvement & improvement \\
     & avg & stdev & avg & stdev \\
    \hline
    \dataset{80-320} & \textbf{0.00072} & 0.00223 & 0.00064 & 0.00218 \\
    \dataset{90-405} & 0.00698 & 0.00616 & \textbf{0.00851} & 0.00659 \\
    \dataset{100-500} & 0.00796 & 0.00797 & \textbf{0.00964} & 0.00804 \\
    \hline
    \dataset{100-100} & 0.00000 & 0.00000 & 0.00000 & 0.00000 \\
    \dataset{100-200} & 0.00000 & 0.00000 & 0.00000 & 0.00000 \\
    \dataset{100-1000} & 0.01710 & 0.01188 & \textbf{0.02337} & 0.01558 \\
  \end{tabular}
\end{table}

TODO interpretation: \heu{Mutation} wins.

@@

TODO with \heu{Mutation} from the previous step, how about using Random as CH? Do we get an improvement?
